---
title: "CLT_WUP"
author: "Gianna Chevez"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

kkardashtemp  see code below

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")

my1000 <- sample(Homers_data , size = 1000, replace=T)

```

```{r}

library(ggplot2)
sampleNumber = sample(1:10000, size = 1000)
library(dplyr)
my1000 <- Homers_data[sampleNumber, ]
names(my1000)
# Basic density
p <- ggplot(my1000, aes(x=kkardashtemp,col=sex)) + 
  geom_density()
p
# Add mean line
p+ geom_vline(aes(xintercept=mean(kkardashtemp)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$kkardashtemp),' sd = ',sd(my1000$kkardashtemp)))
```

In our original dataset with a set standard deviation, when analyzing kKardashtemp and the differences between males and females, it appears that with the number 9, there is a significantly higher uptake in males compared to females, with female ratings very close to zero and male ratings nearing 100. Next, when we examine the number 16, the standard deviation is approximately 10.5, indicating a shift towards a more blended distribution. Following that, with the number 25, the standard deviation decreases to around 8 to 8.5, suggesting that the data is becoming increasingly consolidated, with responses trending towards a consensus and reflecting a clearer preference in the kKardashtemp ratings. Finally, with the number 36, the standard deviation decreases further to around 6.5 to 7, highlighting an even greater level of agreement among respondents and reinforcing the idea that the kKardashtemp ratings are stabilizing as the dataset expands.


```{r}
numb=36
Hdata = Homers_data[sample(1:1000, size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k2 = x.avg

p <- ggplot(my1000, aes(x=k2)) + 
  geom_density() 
p

# Add mean line
  geom_vline(aes(xintercept=mean(k2)),
            color="blue", linetype="dashed", size=1)
print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```
With the number 9, we can observe a peak where males and females influence each other, leaning more towards the left side of the kKardashtemp scale. When analyzing the number 16, the standard deviation is approximately 10.1, and the voting curve becomes less varied and more rounded, with a slight lean to the right, indicating a preference for kKardashtemp. The standard deviation for the number 25 is around 8 to 8.5, reflecting the ongoing progression of the graph. Finally, with the number 36, the standard deviation further decreases to around 6.5 to 7, 
highlighting an even greater level of consensus among respondents. This continued reduction in variability reinforces the notion that the kKardashtemp ratings are stabilizing, with participants showing a clear and consistent preference as the dataset expands.



```{r}
numb = 36
Hdata = Homers_data[sample(1:1000,size=numb*1000, replace=T),"kkardashtemp"]
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
my1000$k36 = x.avg


p <- ggplot(my1000, aes(x=k36),col=sex) + 
  geom_density() +

# Add mean line
 geom_vline(aes(xintercept=mean(k36)),
            color="blue", linetype="dashed", size=1)
p + ggtitle("n = 4") +
  xlab("temperature") + ylab(" density")

print(paste('mean = ', mean(my1000$k36),' sd = ',sd(my1000$k36)))

```

Unlike the previous graph, which exhibited greater variability, this new graph with a standard deviation of approximately 14 and the number 9 appears more blended, featuring smaller loops compared to the pronounced dips observed with the previous number 5. With the number 16, the graph shows less inclination towards any side, indicating a consensus in the middle and a peak, although it still trends more towards the right. When we analyze the number 25, the standard deviation decreases further to around 8 to 8.5, suggesting that the data is becoming increasingly consolidated. This trend indicates a stronger agreement among responses, with kKardashtemp ratings reflecting a more definitive preference as the sample size increases. Finally, with the number 36, the standard deviation further decreases to around 6.5 to 7, highlighting an even greater level of consensus among respondents. This continued reduction in variability reinforces the notion that the kKardashtemp ratings are stabilizing, with participants showing a clear and consistent preference as the dataset expands.





